\chapter{Introduction}
On this project our purpose is to save navigation data (latitude, longitude, altitude, accuracy, speed) collected from GPS of mobile device and show the route of a trip on the map. There will be a mobile application and server side application to provide some features, lets users to share trips, review trips, communicate and socialize with each others. Various media records such as photos, videos and sound recorded from mobile device during the trip will be associated with the route. There will be a team trip option for the trips which includes more than one member. Team trip option lets every team member to see any other team member's location simultaneously if there is an Internet connection. In order to determine travelling method, using the temporal changes of the navigation data taken from the GPS, average and instant speed will be calculated. As result, trip type will be labelled as vehicle trip, walking trip, running trip or cycling trip using calculated speed data. In order to provide interaction between users a social media environment will be designed. People will be able to establish their friendship here. In the news flow, there will be a timeline section. Posts which are shared by friends of users will be shown there. The trips can be liked by other users in the news flow, they can leave a comment on trip or the users can follow trips they like by downloading it on their own mobile device. Users can create complaints about comments, other user profiles and trips. Complaints are evaluated by the system administrators. If admins think that regarding complaint are right, the content can be hidden.
\section{Literature Review}
The purpose to realize that project is to simplify planning, recording and sharing traveler's trips. We know that it is not easy to organize photos and media taken on a trip and later on sharing them on any social media or personal blogs. In any marketplaces including play store and appstore there are lots of applications for tracking and planning travel but most of them only saves location data and do not include media or user notes. There are only a few remarkable application which saves location data, media and also provides a social media enviroment. However there is no application that provides trip tracking, organizing media, following other person's route, sharing memories and also doing all of these with friends at the same time. 

\section{Objective of the Thesis}
For travelers it is not easy to organize media and associate media with saved locations. Also if trip has been organized with more than one person it is also difficult to merge media and organize additional material prior to share on any social media enviroment or on the Internet. It's important to say that every member of team has him/her own memory which is important and it must be saved.

\section{Hypothesis}
To do that it is neccessary to store locations data, store media and associate them with their location and store them with everthing in a trip. So that people can remember a every single detail of their trip.