\chapter{General Information}
The main purpose of this section to review projects that are already developed by others which have similarities with ours.
\section{Trip Tracker (Android application)}
Trip Tracker\cite{triptracker}, a Microsoft Garage project, is a free application that automatically records your drives, runs, walks, and bike rides. This application has developed with LOOP \cite{loop}. This application can only track, store user's location and show stored data on the map.

\section{Route Tracker (Android application)}
Route Tracker \cite{routetracker} is a GPS application for tracking/loading routes in your android mobile phone that gives you a real time response on your location. It supports GPX tracks file import, GPX/KML/google map embedded HTML file export, sync workouts with RunKeeper account, auto-Lap for each mile/kilometer, audio reminder for auto lap time reminding, vibration for auto lap, sharing to friends, open street view for record locations, duration, distance, pace and calories indication.

\section{Polarsteps - Travel Tracker (Android and Ios application)}
Polarsteps \cite{polarsteps} can provide tracking location of user, can show media as just photo and video on the trip path. They are claiming that it is a low power consuming application. User can use this application only for their personal trips. It is not possible to organize team trips. This application also provides a social media platform. Social media enviroment could only usable for sharing trips and comment on shared content. It is not possible to download and track any shared route.

\section{Maps (Android and Ios application)}
Google Maps \cite{googlemap} can save user's location continuosly. In this application there is no start trip option. This application determines kind of trip automaticaly. This application is not developed to track, it is developed to navigate users. User can watch his/her activity on the menu named 'TimeLine'. On users timeline any photos and videos are shown, there is no audio or text notes support. In this application social media or sharing trip option do not exist.

Gezi Yorum offers an extended trip tracking and organizing system. Gezi Yorum will include all of the feautures of the applications listed above and in addition Gezi Yorum will able to organize team trips and following member on a trip. Table~\ref{spec} shows specifications of applications.
\begin{table}[!ht]
\centering
\caption{Specifications of Applications}
\label{spec}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
\text{Specification} & \text{Trip Tracker} & \text{Route Tracker} & \text{Polarsteps} & \text{Maps} 
& \text{Gezi Yorum} \\ \hline
Record trip & + & + & + & + & + \\ \hline
Show trip on map & + & + & + & + & + \\ \hline
Trip type & + & + & + & + & + \\ \hline
Media on location & - & - & + & - & + \\ \hline
Social media & - & - & + & - & + \\ \hline
Personal trip & + & + & + & - & + \\ \hline
Team trip & - & - & - & - & + \\ \hline
Live tracking & - & - & - & - & + \\ \hline
\end{tabular}
\end{table}