\chapter{Conclusion}

	With this project developed, the trips can be recorded by using mobile application and can be shown by using both mobile and web applications. For users, system is developed to manage trips to save time and effort. Users can save videos, photos, audios along to the route. The trips can be categorized as single and group. For single trips, only one user can create his or her own trip, can save the route and attach media to the path. For group trips, application allows users same functionality as single trip's in addition to that they can see each others locations simultaneously, trip participants can combine saved trip media to the creator user's media. Application can guess what the type of the trip by processing the speed and accuracy of the GPS signals received, there are 4 labels for that, these are walking, running, bicycle and riding. Users can share the created trips with the other users. They can choose privacy of trip content which can be only me, only my friends and everybody. This application will offer users a practical solution to save the time spent on sharing a trip on any social media environment or on the Internet, because it contains a social media platform inside. Users can add other users as friends to be able to contact with them and to be able to see the trips they participated, created and shared. Users can interact with other users, they can like or comment each others trips, if they think the trip has inappropriate content they can create a complaint. Complaints are evaluated by the administrators of the system. Administrators have right to hide them if they think the complainant is right. Users can also search trips depending upon the type, location or creator of it, they can also search for other users. Users can download the trips to their mobile device that are created by other users if they want, by downloading them they can prefer to follow the route same as downloaded one, or they can see the path of downloaded trip, monitor it but create a totally new one and use the downloaded one as a guide, application allows users every functionality even though user prefer to follow the downloaded one.

	The project is suitable for used by travel agecys, city municipalities for advertising tourist attraction places and also building a trip guide for people.

	The project could be improved with more complex social media platform which includes extensive trip search system, trip recommendation system, messaging system. Also mobile application could be improved with getting more details about trip like step count during trip, developing a better tracking system, implementing augmented reality features to application, improving compressing performance of trip files and using push notifications. These are evaluated and are among our future works.

